\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-28 paper/experiments.tex
Add SMAPE citation

\subsection{Results}

@@

\Cref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error (SMAPE) for \ProjectName{}'s query results when compared to running
imputation on the base tables and executing the query on this cleaned base data \todo{SMAPE citation}.
Each query was separately run 200 times in both settings and then results from the two approaches were paired up and compared tuple-wise.
We average tuple-wise absolute percentage deviations within each iteration of a query, and we report this value averaged over all iterations.
We can see that optimizing for quality indeed reduces the SMAPE of query results.
In general, the SMAPE relative to the base-imputation approach are low in all cases --- between \lowsmapealphazero{} and \highsmapealphaoneexacs{} percent ---, indicating that on-the-fly imputation produces
similar results to imputation at the base tables.

>>>>

\subsection{Results}\label{sec:results}

@@

\Cref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error (SMAPE) for
\ProjectName{}'s query results when compared to running imputation on the base tables and
executing the query on this cleaned base data \cite{tofallis2015better}.  Each query was
separately run 200 times in both settings and then results from the two approaches were
paired up and compared tuple-wise.  We average tuple-wise absolute percentage deviations
within each iteration of a query, and we report this value averaged over all iterations.  We
can see that optimizing for quality indeed reduces the SMAPE of query results.  In general,
the SMAPE relative to the base-imputation approach are low in all cases --- between
\lowsmapealphazero{} and \highsmapealphaoneexacs{} percent ---, indicating that on-the-fly
imputation produces similar results to imputation at the base tables.
